\textit{Supplemental figures for}: A Gaussian process model of human electrocorticographic data

### 2020-01-21 paper/main.tex
updates to stability code and pdf

\newcommand{\perexpcorrmaps}{S1}
\newcommand{\perexptaskrecon}{S2}
\newcommand{\perexptaskreconseparated}{S3}
\newcommand{\suppstats}{S4}
\newcommand{\intersectmap}{S5}

@@

A second mechanism whereby a given region $x$ can contribute to the
recording at $\eta$ is through (direct or indirect) anatomical
connections between structures near $x$ and $\eta$.  We use temporal
correlations in the data to estimate these anatomical
connections~\citep{BeckEtal18}.  Let $\bar{R}$ be the set of locations
at which we wish to estimate local field potentials, and let
$R_{s} \subseteq \bar{R}$ be set of locations at which we observe local
field potentials from patient $s$ (excluding the electrodes that did
not pass the kurtosis test described above). In the analyses below we
define $\bar{R} = \cup_{s=1}^S R_s$.  We can calculate the expected
inter-electrode correlation matrix for patient $s$, where
$C_{s,k}(i,j)$ is the correlation between the time series of voltages
for electrodes $i$ and $j$ from subject $s$ during session $k$, using:

@@

We designed our approach to be agnostic to electrode impedances, as
electrodes that do not exist do not have impedances.  Therefore our
algorithm recovers voltages in standard deviation ($z$-scored) units
rather than attempting to recover absolute voltages. (This property
reflects the fact that $\hat{K}_{\beta_s, \alpha_s}$ and
$\hat{K}_{\alpha_s, \alpha_s}$ are correlation matrices rather than
covariance matrices.)  Also, we note that
Equation~\ref{eqn:reconstruction} requires computing a $T$ by $T$
matrix, which can become computationally intractable when $T$ is very
large (e.g., for the patient highlighted in Fig.~\ref{fig:recon}, $T =
12786750$). However, because Equation~\ref{eqn:reconstruction} is time
invariant, we may compute $Y_{s,k,\beta_s}$ in a piecewise
manner by filling in $Y_{s,k,\beta_s}$ one row at a time (using the
corresponding samples from $Y_{s, k, \alpha_s}$).

@@

%correlations by brain area, distribution of correlations
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/corrmap}
  \caption{\textbf{Reconstruction quality across all electrodes in two
      ECoG datasets.}  \textbf{A. Distributions of correlations
      between observed versus reconstructed activity by electrode, for
      Dataset 1.}  The across-patient distribution (black) reflects
    reconstruction accuracy (correlation) using a correlation model
    learned from all but one patient's data, and then applied to that
    held-out patient's data.  The within-patient distribution (gray)
    reflects performance using a correlation model learned from the same
    patient who contributed the to-be-reconstructed electrode.
    \textbf{B. Distributions of correlations for Dataset 2.}  This
    panel is in the same format as Panel A, but reflects results
    obtained from Dataset 2.  The histograms aggregate data across
    both Dataset 2 experiments; for results broken down by experiment
    see Figure~\perexptaskreconseparated. \textbf{C.--D.  Reconstruction
      performance by location.} The colors denote the average across-session
    correlation, using the across-patient correlation model, between
    the observed and reconstructed activity at the given electrode
    location projected to the cortical surface.}
  \label{fig:corrmap}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/informap}
  \caption{\textbf{Most informative electrode locations.}
    \textbf{A. Dataset 1 information score by voxel.} The voxel colors
    reflect the weighted average reconstruction accuracy across all
    electrodes from any patients with at least one electrode within 20
    MNI units of the given voxel.  \textbf{B. Dataset 2 information
      score by voxel.}  This panel is in the same format as Panel A.
    In both panels the contours indicate the intersections between the
    top 10\% most informative voxels in each map (also see
    Fig.~\intersectmap).  \textbf{C. Intersection.}  
    Gray areas indicate the intersections between the
    top 10\% most informative voxels in each map.  \textbf{D. Correspondence in information
      scores by voxel across Datasets 1 and 2.}  Same format as
    Figure~\ref{fig:density}C.}
  \label{fig:informap}
\end{figure}

We also wondered what frequency properties contributed to the
reconstruction accuracy.  For this analysis, we INSTERT TUDORS
DESCRIPTION FOR FREQ ANALYSIS.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/frequency}
  \caption{\textbf{Reconstruction quality across all electrodes in two
      ECoG datasets for each frequency band.}  \textbf{A. Distributions of correlations
      between observed versus reconstructed activity by electrode, for
      each frequency band in Dataset 1.}  The across-patient
    distribution (left jitter barplot) reflects
    reconstruction accuracy (correlation) using a correlation model
    learned from all but one patient's data, and then applied to that
    held-out patient's data.  The within-patient distribution (right
    jitter barplot in lighter color)
    reflects performance using a correlation model learned from the same
    patient who contributed the to-be-reconstructed electrode.
    \textbf{B.~Statistical summary of across-patient reconstruction
      quality by electrode for each frequency band in Dataset 1.} In the upper triangles of each
    map, warmer colors (positive t-values) indicate that the
    distribution of
    reconstruction accuracy for the frequency band in a given row
    yielded was greater than the frequency band in the given
    column. Cooler colors (negative t-values) indicate that the
    frequency band in the given row yielded lower reconstruction
    accuracy than the frequency band in the given column. The lower
    triangles of each map denote the corresponding p-values for the
    t-tests. The diagonal entries display the relative average
    reconstruction accuracy given to each frequency band. \textbf{C.~Statistical summary ofwithin-patient reconstruction
      quality by electrode for each frequency band in Dataset 1.}
    This panel displays the within-patient statistical summary,
    in the same format as Panel B.  \textbf{D.~Distributions of correlations
      between observed versus reconstructed activity by electrode, for
      each frequency band in Dataset 2.}  This panel displays
    reconstruction accuracy distributions for each frequency band for
    Dataset 2 in
    the same format as Panel A. \textbf{E.~Statistical summary of
      across-patient reconstruction quality by electrode for each
      frequency band in Dataset 2.} This is the same format as Panel
    B for Dataset 2. \textbf{F.~Statistical summary of
      within-patient reconstruction quality by electrode for each
      frequency band in Dataset 2.}This is the same format as Panel
    C for Dataset 2.}
  \label{fig: frequency}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/networks}
  \caption{\textbf{Electrode sampling density by location.}
    \textbf{A.~Electrode sampling density by voxel in Dataset 1.} Each
    voxel is colored by the proportion of total electrodes in the
    dataset that are
    located within a 20~MNI unit radius sphere centered on the given
    voxel.  \textbf{B.~Electrode sampling density by voxel in Dataset
      2.}  This panel displays the sampling density map for Dataset 2,
    in the same format as Panel A.  \textbf{C.~Correspondence in
      sampling density by voxel across Datasets 1 and 2.}  The
    two-dimensional histogram displays the by-voxel densities in the
    two Datasets, and the one-dimensional histograms display the
    proportions of voxels in each dataset with the given density
    value.  The correlation reported in the panel is across voxels in
    the 4~mm$^3$ MNI brain.}
  \label{fig: networks}
\end{figure}

@@

One potential limitation of our approach is that it does not provide a
natural means of estimating the precise timing of single-neuron action
potentials.  Prior work has shown that gamma band and broadband
activity in the LFP may be used to estimate the firing rates of
neurons that underly the population contributing to the
LFP~\citep{MillEtal08, MannEtal09, JacoEtal10b, CronEtal11}.  Because
SuperEEG reconstructs LFPs throughout the brain, one could in
principle use gamma or broadband power in the reconstructed signals to
estimate the corresponding firing rates (though not the timings of
individual action potentials).

>>>>

\newcommand{\perexpcorrmaps}{S1}
\newcommand{\perexptaskrecon}{S2}
\newcommand{\perexptaskreconseparated}{S3}
\newcommand{\freqpower}{S4}
\newcommand{\networkpower}{S5}
\newcommand{\suppstats}{S6}

@@

A second mechanism whereby a given region $x$ can contribute to the
recording at $\eta$ is through (direct or indirect) anatomical
connections between structures near $x$ and $\eta$.  Although
anatomical and function correlations can differ
markedly~\citep[e.g.,][]{AdacEtal11, HoneEtal09, GoniEtal14}, we use temporal
correlations in the data to estimate these anatomical
connections~\citep{BeckEtal18}.  Let $\bar{R}$ be the set of locations
at which we wish to estimate local field potentials, and let
$R_{s} \subseteq \bar{R}$ be set of locations at which we observe local
field potentials from patient $s$ (excluding the electrodes that did
not pass the kurtosis test described above). In the analyses below we
define $\bar{R} = \cup_{s=1}^S R_s$.  We can calculate the expected
inter-electrode correlation matrix for patient $s$, where
$C_{s,k}(i,j)$ is the correlation between the time series of voltages
for electrodes $i$ and $j$ from subject $s$ during session $k$, using:

@@

We designed our approach to be agnostic to electrode impedances, as
electrodes that do not exist do not have impedances.  Therefore our
algorithm recovers voltages in standard deviation ($z$-scored) units
rather than attempting to recover absolute voltages. (This property
reflects the fact that $\hat{K}_{\beta_s, \alpha_s}$ and
$\hat{K}_{\alpha_s, \alpha_s}$ are correlation matrices rather than
covariance matrices.)  Also, we note that
Equation~\ref{eqn:reconstruction} requires computing a $T$ by $T$
matrix, which can become computationally intractable when $T$ is very
large (e.g., for an example patient in Dataset 1, $T =
12786750$). However, because Equation~\ref{eqn:reconstruction} is time
invariant, we may compute $Y_{s,k,\beta_s}$ in a piecewise
manner by filling in $Y_{s,k,\beta_s}$ one row at a time (using the
corresponding samples from $Y_{s, k, \alpha_s}$).

@@

%correlations by brain area, distribution of correlations
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/corrmap}
  \caption{\textbf{Reconstruction quality across all electrodes in two
      ECoG datasets.}  \textbf{A. Distributions of correlations
      between observed versus reconstructed activity by electrode, for
      Dataset 1.}  The across-patient distribution (black) reflects
    reconstruction accuracy (correlation) using a correlation model
    learned from all but one patient's data, and then applied to that
    held-out patient's data.  The within-patient distribution (gray)
    reflects performance using a correlation model learned from the same
    patient who contributed the to-be-reconstructed electrode.
    \textbf{B. Distributions of correlations for Dataset 2.}  This
    panel is in the same format as Panel A, but reflects results
    obtained from Dataset 2.  The histograms aggregate data across
    both Dataset 2 experiments; for results broken down by experiment
    see Figure~\perexptaskreconseparated. \textbf{C.--D.  Reconstruction
      performance by location.} The colors denote the average across-session
    correlation, using the across-patient correlation model, between
    the observed and reconstructed activity at the given electrode
    location projected to the cortical surface~\citep{CombEtal19}.}
  \label{fig:corrmap}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/informap}
  \caption{\textbf{Most informative electrode locations.}
    \textbf{A. Dataset 1 information score by voxel.} The voxel colors
    reflect the weighted average reconstruction accuracy across all
    electrodes from any patients with at least one electrode within 20
    MNI units of the given voxel.  \textbf{B. Dataset 2 information
      score by voxel.}  This panel is in the same format as Panel A.
    In both panels the contours indicate the intersections between the
    top 10\% most informative voxels in each map (also see
    Fig.~\networks Panels A.-C. All for networks within this region).  \textbf{C. Intersection.}  
    Gray areas indicate the intersections between the
    top 10\% most informative voxels in each map and projected onto the cortical surface~\citep{CombEtal19}. \textbf{D. Correspondence in information
      scores by voxel across Datasets 1 and 2.}  Same format as
    Figure~\ref{fig:density}C.}
  \label{fig:informap}
\end{figure}

We also wondered what frequency properties contributed to the
reconstruction accuracy. To recover frequency-band specific voltage activity
from each recording, a second-order Butterworth filter was applied
across bands $\delta$, $\theta$, $\alpha$, $\beta$, $\gamma_L$, and
$\gamma_H$ with respective frequency ranges 2-4 Hz, 4-8 Hz, 8-12 Hz,
12-30 Hz, 30-60 Hz, and 60-100 Hz. Bandpass signals contain
information about the phase and amplitude of the underlying frequency
band, providing the most detailed view of the activity at that
frequency. Additionally, we calculated the reconstruction accuracies
using power at each band by taking the absolute
value of the Hilbert tranform of the bandpassed signal (see Fig.~\freqpower). To compute the broadband power (BB), we
first computed instantaneous power at 50 log-spaced frequencies
between 2 and 100 Hz using Morlet wavelets (n=4). Then, for each time
point and electrode, we fitted a robust Huber regression to frequency
and power in log-space, and calculated the mean height of the
resulting line. We then followed the same procedure outlined above
(see Fig.~\ref{fig:methods}) to
obtain the reconstruction accuracy at each bandpassed frequency as well
as broadband power for both datasets (see Fig.~\ref{fig:frequency}).
We found
the best average reconstruction accuracy for each dataset was obtained using broadband
power, which is a correlate of neural firing
~\citep{MannEtal09}. We also found a similar trend in reconstruction
accuracy for frequency bands across the two datasets, performing better at lower
frequencies (peaking at $\alpha$) and worst at high frequencies.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/frequency}
  \caption{\textbf{Reconstruction quality across all electrodes in two
      ECoG datasets for each frequency band.} \textbf{A. Distributions of correlations
      between observed versus reconstructed activity by electrode, for
      each frequency band in Dataset 1.}  The across-patient
    distribution (left jitter barplot) reflects
    reconstruction accuracy (correlation) using a correlation model
    learned from all but one patient's data, and then applied to that
    held-out patient's data.  The within-patient distribution (right
    jitter barplot in lighter color)
    reflects performance using a correlation model learned from the same
    patient who contributed the to-be-reconstructed electrode, colored
    by frequency and includes the raw voltages displayed in
    Fig.~\ref{fig:corrmap}A in gray.
    \textbf{B.~Statistical summary of across-patient reconstruction
      quality by electrode for each frequency band in Dataset 1.} In the upper triangles of each
    map, warmer colors (positive t-values) indicate that the
    distribution of
    reconstruction accuracy for the frequency band in a given row
    yielded was greater than the frequency band in the given
    column. Cooler colors (negative t-values) indicate that the
    frequency band in the given row yielded lower reconstruction
    accuracy than the frequency band in the given column. The lower
    triangles of each map denote the corresponding p-values for the
    t-tests. The diagonal entries display the average
    reconstruction accuracy given to each frequency
    band. \textbf{C.~Statistical summary of within-patient reconstruction
      quality by electrode for each frequency band in Dataset 1.}
    This panel displays the within-patient statistical summary,
    in the same format as Panel B.  \textbf{D.~Distributions of correlations
      between observed versus reconstructed activity by electrode, for
      each frequency band in Dataset 2.}  This panel displays
    reconstruction accuracy distributions for each frequency band for
    Dataset 2. \textbf{E.~Statistical summary of
      across-patient reconstruction quality by electrode for each
      frequency band in Dataset 2.} This is the same format as Panel
    B for Dataset 2. \textbf{F.~Statistical summary of
      within-patient reconstruction quality by electrode for each
      frequency band in Dataset 2.}This is the same format as Panel
    C for Dataset 2.}
  \label{fig:frequency}
\end{figure}

We also wanted to see how the most informative regions changed by
frequency. Lower frequency oscillations, such as delta, theta, and alpha, have
been posited to be processing modes which span large swaths of
cortical regions and are thought to serve the purpose of integration
across many cortical sites ~\citep{Knya12}. Higher frequency
oscillations such as beta and gamma, are more limited to topographic
area ~\citep{Nune95}, and are modulated by slow oscillations
hierarchically ~\citep{EngeEtal10}. Using the frequency-specific reconstruction accuracies, we
followed the process outlined in Fig.~\ref{fig:informap}C, to obtain
the most informative locations for each frequency.  When we examined the intersection
between the top 10\% most informative voxels across the two datasets
for each bandpassed frequency, we found a somewhat consistent hierarchical
structure (see Fig.~\ref{fig:networks}E).

We then wondered which
networks were involved in each of
these frequency-specific intersecting regions.  To better understand the networks involved
we colored the regions (Fig.~\ref{fig:networks}A) based on the
network parcellation ~\citep[using $k$=7;][]{YeoEtal11}} (Fig.~\ref{fig:networks}D) and calculated the proportion of each
of those networks (Fig.~\ref{fig:networks}B).  Consistent with the idea outlined
above, we found networks most involved in the lowest frequency band,
$\delta$, were networks involved integration and global processing
(specifically the dorsal attention ~\citep{MarzEtal13}, default mode,
and frontoparietal networks).  Although these networks are also seen
in the $\theta$ intersection, they are less proportionally to the
visual network.  Alpha power is consistently modulated in EEG studies
of attention and visuo-motor ~\citep{MartiEtal10, MarzEtal13}, and we
similarly found a high proportion of visual and somatomotor networks
within this band.  We found $\beta$ intersections to predominantly
consist of somatomotor network, consistent with~\citep{RittEtal08,
  VanEEtal11}.  Also consistent with heavily cited
literature~\citep{FrieEtal07}, the network most predominant in the
$\gamma$ intersection was the visual network.  Lastly, broadband power
was found predominantly in frontoparietal and default mode networks,
consistent with ~\{OssaEtal11}.  We then carried out a
meta analysis using Neurosynth~\citep{RubiEtal17} to identify the 5
terms most commonly associated with the given map
(Fig.~\ref{fig:networks}C).

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/networks}
  \caption{\textbf{Most informative electrode locations by frequency
      and the networks involved.}
    \textbf{A.~Intersections across datasets for each frequency.} The
    inflated brain plots display the intersections between the
    top 10\% most informative voxels were calculated as described in Fig.~\ref{fig:informap}
    for each frequency and projected onto the cortical surface~\citep{CombEtal19}. Intersecting voxels are colored according to the 7 networks
    from~\citep{YeoEtal11}.
    \textbf{B.~Proportion of networks in most informative electrode locations by
    frequency.}  Pie graphs display the proportion of the 7 networks
  ~\citep{YeoEtal11} in the most informative locations by
  frequency, and are sized relative to the average reconstruction
  accuracy for each frequency. \textbf{C.~Terms associated with most informative
    electrode locations.}  The
    lists of terms display the top five Neurosynth
    terms~\citep{RubiEtal17} decoded from the corresponding brain
    maps, and colored according the frequency (see Panel
    E legend). \textbf{D.~Network parcellation from~\citep{YeoEtal11}.}
    Seven network parcellation as described
    in~\citep{YeoEtal11}. \textbf{E.~Most informative locations by
      frequency.} The inflated brain plot displays the locations of
    the most informative locations (Panel A), colored by frequency,
    and projected onto the cortical surface~\citep{CombEtal19}.}
  \label{fig:networks}
\end{figure}

@@

One potential limitation of our approach is that it does not provide a
natural means of estimating the precise timing of single-neuron action
potentials.  Prior work has shown that gamma band and broadband
activity in the LFP may be used to estimate the firing rates of
neurons that underly the population contributing to the
LFP~\citep{MillEtal08, MannEtal09, JacoEtal10b, CronEtal11}.  Because
SuperEEG reconstructs LFPs throughout the brain, one could in
principle use broadband power in the reconstructed signals to
estimate the corresponding firing rates (though not the timings of
individual action potentials). Interestingly, our frequency-specific
analysis yielded the best reconstruction accuracies using broadband
power.

### 2020-01-21 paper/supporting_information.tex
updates to stability code and pdf

\title{\textit{Supplemental figures for}: A Gaussian process model of human electrocorticographic data} 
\author{
  Lucy L. W. Owen$^{1}$,
  Andrew C. Heusser$^{1, 2}$, and
  Jeremy R. Manning$^{1\ast}$\\\\
$^{1}$Department of Psychological and Brain Sciences, Dartmouth College,\\
Hanover, NH 03755, USA\\
$^{2}$Akili Interactive,\\
Boston, MA 02110, USA}

@@

\begin{document}
\maketitle

@@

\begin{figure}[b!]
\centering
\includegraphics[width=0.6\textwidth]{figs/supplemental_1}
\caption{\textbf{Reconstruction quality for Datasets 1 and 2.}
  \textbf{A. Distributions of correlations between observed versus
    reconstructed activity by electrode, for Dataset 1.} The split
  violin plot reflects the same data as Figure~3A, presented here for
  comparison.  \textbf{B. Distributions of correlation between
    observed versus reconstructed activity by electrode, for Dataset
    2.}  The left-most split violin plot (``Within'') reflects the
  same data as Figure~3B, presented here for comparison.  The
  ``Across'' plot reflects the same analyses, but limited to models
  that were trained and tested on \textit{different} Dataset 2
  experiments.  The ``All'' plot reflects the same analyses, but
  including models that were trained and tested on both of the Dataset
  2 experiments.  All plots: the dark gray distributions denote
  across-subject correlations (model trained on all but one patient
  and tested on the held-out patient), and the medium gray
  distributions denote within-subject correlations (model trained on
  all but one electrode from one patient, and tested on the held-out
  electrode).  The horizontal bars denote $t$-tests between the
  corresponding distributions (after $z$-transforming the
  correlations), and the white numbers reflect the distribution means.
  The symbols denote the corresponding $p$-values of those statistical
  tests.}
\label{fig:supplemental_1}
\end{figure}

@@

\begin{figure}[p]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_3}
\caption{\textbf{Reconstruction quality across all electrodes in two
      Dataset 2 experiments.}  \textbf{A. Distributions of correlations
      between observed versus reconstructed activity by electrode, for
      Experiment 1.}  Same format as Figure~3A and B, but reflects data shown
    in Figure~\ref{fig:supplemental_2}A (leftmost violin plot).
 \textbf{B. Distributions of correlations
      between observed versus reconstructed activity by electrode, for
      Experiment 2.}  Same format as Figure~3A and B, but reflects
    data shown in Figure~\ref{fig:supplemental_2}B (leftmost violin
    plot).  \textbf{C.--D.  Reconstruction
      performance by location.} Each dot reflects the location of a
    single implanted electrode from Dataset 2, Experiment 1 (Panel C)
    or Dataset 2, Experiment 2 (Panel D).  The dot colors denote the
    average within-experiment (across-session)
    correlation, using the across-patient correlation model, between
    the observed and reconstructed activity at the given electrode
    location.}
\label{fig:supplemental_3}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_4}
\caption{\textbf{Reconstruction accuracy versus within-subject data
    features for two ECoG datasets.} \textbf{A.--F.  Features from
    Dataset 1.}  Features include: (\textbf{A.}) total number of
  electrodes implanted in each patient's brain, (\textbf{B.})
  per-patient number of electrodes that were filtered out due to
  having an maximum kurtosis greater than 10 across all recording
  sessions, (\textbf{C.})  per-patient proportion of electrodes that
  were filtered out due to having an average kurtosis greater than 10,
  (\textbf{D.})  per-patient number of recording sessions,
  (\textbf{E.}) per-patient total recording time (h), and
  (\textbf{F.}) per-patient average session length (h).
  \textbf{G.--L. Features from Dataset 2.}  Analogous format to Panels
  A--F.}
\label{fig:supplemental_4}
\end{figure}

\begin{figure}[ptb]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_5}
\caption{\textbf{Most informative electrode locations.}  This map
  shows the region outlined in white from Figure~5 in greater detail.
  Across Datasets 1 and 2, electrodes in these locations were
  identified as yielding the (10\%) best reconstruction accuracies at
  \textit{other} locations throughout the brain.  The $x$-coordinates
  in each panel denote the positions of the sagittal slices in MNI space.}
\label{fig:supplemental_5}
\end{figure}

% \newpage
% \renewcommand{\refname}{Supplemental references}
% \bibliography{memlab}

>>>>

\title{\textit{Supplemental figures for}: A Gaussian process model of human electrocorticographic data} 
\author{
  Lucy L. W. Owen$^{1}$,
  Tudor A. Muntianu$^{1}$,
  Andrew C. Heusser$^{1, 2}$, \\
  Patrick Daly$^{3}$,
  Katherine Scangos$^{3}$, and
  Jeremy R. Manning$^{1\ast}$\\\\
$^{1}$Department of Psychological and Brain Sciences, Dartmouth College,\\
Hanover, NH 03755, USA\\
$^{2}$Akili Interactive,\\
Boston, MA 02110, USA}

@@

\begin{document}

\begin{titlepage}
  \maketitle
  \end{titlepage}

@@

\begin{figure}[b!]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_1}
\caption{\textbf{Reconstruction quality for Datasets 1 and 2.}
  \textbf{A. Distributions of correlations between observed versus
    reconstructed activity by electrode, for Dataset 1.} The split
  violin plot reflects the same data as Figure~3A, presented here for
  comparison.  \textbf{B. Distributions of correlation between
    observed versus reconstructed activity by electrode, for Dataset
    2.}  The left-most split violin plot (``Within'') reflects the
  same data as Figure~3B, presented here for comparison.  The
  ``Across'' plot reflects the same analyses, but limited to models
  that were trained and tested on \textit{different} Dataset 2
  experiments.  The ``All'' plot reflects the same analyses, but
  including models that were trained and tested on both of the Dataset
  2 experiments.  All plots: the dark gray distributions denote
  across-subject correlations (model trained on all but one patient
  and tested on the held-out patient), and the medium gray
  distributions denote within-subject correlations (model trained on
  all but one electrode from one patient, and tested on the held-out
  electrode).  The horizontal bars denote $t$-tests between the
  corresponding distributions (after $z$-transforming the
  correlations), and the white numbers reflect the distribution means.
  The symbols denote the corresponding $p$-values of those statistical
  tests.}
\label{fig:supplemental_1}
\end{figure}

@@

\begin{figure}[p]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_3}
\caption{\textbf{Reconstruction quality across all electrodes in two
      Dataset 2 experiments.}  \textbf{A. Distributions of correlations
      between observed versus reconstructed activity by electrode, for
      Experiment 1.}  Same format as Figure~3A and B, but reflects data shown
    in Figure~\ref{fig:supplemental_2}A (leftmost violin plot).
 \textbf{B. Distributions of correlations
      between observed versus reconstructed activity by electrode, for
      Experiment 2.}  Same format as Figure~3A and B, but reflects
    data shown in Figure~\ref{fig:supplemental_2}B (leftmost violin
    plot).  \textbf{C.--D.  Reconstruction
      performance by location.} Each dot reflects the location of a
    single implanted electrode from Dataset 2, Experiment 1 (Panel C)
    or Dataset 2, Experiment 2 (Panel D).  The dot colors denote the
    average within-experiment (across-session)
    correlation, using the across-patient correlation model, between
    the observed and reconstructed activity at the given electrode
    location projected to the cortical surface~\citep{CombEtal19}.}
\label{fig:supplemental_3}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_4}
\caption{\textbf{Reconstruction quality across all electrodes in two
      ECoG datasets for each frequency band.} \textbf{A. Distributions of correlations
      between observed versus reconstructed activity by electrode, for
      each frequency band in Dataset 1.} Same format as Figure~5A, but
    using power at each frequency.
    \textbf{B.~Statistical summary of across-patient reconstruction
      quality by electrode for each frequency band in Dataset 1.} Same format as Figure~5B, but
    using power at each frequency.\textbf{C.~Statistical summary of within-patient reconstruction
      quality by electrode for each frequency band in Dataset 1.}
    This panel displays the within-patient statistical summary,
    in the same format as Panel B.  \textbf{D.~Distributions of correlations
      between observed versus reconstructed activity by electrode, for
      each frequency band in Dataset 2.}  This panel displays
    reconstruction accuracy distributions for each frequency band for
    Dataset 2. \textbf{E.~Statistical summary of
      across-patient reconstruction quality by electrode for each
      frequency band in Dataset 2.} This is the same format as Panel
    B for Dataset 2. \textbf{F.~Statistical summary of
      within-patient reconstruction quality by electrode for each
      frequency band in Dataset 2.}This is the same format as Panel
    C for Dataset 2.}
\label{fig:supplemental_4}
\end{figure}

\begin{figure}[ptb]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_5}
\caption{\textbf{Most informative electrode locations by frequency
      and the networks involved.}
    \textbf{A.~Intersections across datasets for each frequency.}  Same format as Figure~6A, but
    using power at each frequency.
    \textbf{B.~Proportion of networks in most informative electrode locations by
    frequency.}  Pie graphs display the proportion of the 7 networks
  ~\citep{YeoEtal11} in the most informative locations by
  frequency, and are sized relative to the average reconstruction
  accuracy for each frequency. \textbf{C.~Terms associated with most informative
    electrode locations.}  The
    lists of terms display the top five Neurosynth
    terms~\citep{RubiEtal17} decoded from the corresponding brain
    maps, and colored according the frequency (see Panel
    E legend). \textbf{D.~Network parcellation from~\citep{YeoEtal11}.}
    Seven network parcellation as described
    in~\citep{YeoEtal11}. \textbf{E.~Most informative locations by
      frequency.} The inflated brain plot displays the locations of
    the most informative locations (Panel A), colored by frequency,
    and projected onto the cortical surface~\citep{CombEtal19}.}
\label{fig:supplemental_5}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_6}
\caption{\textbf{Reconstruction accuracy versus within-subject data
    features for two ECoG datasets.} \textbf{A.--F.  Features from
    Dataset 1.}  Features include: (\textbf{A.}) total number of
  electrodes implanted in each patient's brain, (\textbf{B.})
  per-patient number of electrodes that were filtered out due to
  having an maximum kurtosis greater than 10 across all recording
  sessions, (\textbf{C.})  per-patient proportion of electrodes that
  were filtered out due to having an average kurtosis greater than 10,
  (\textbf{D.})  per-patient number of recording sessions,
  (\textbf{E.}) per-patient total recording time (h), and
  (\textbf{F.}) per-patient average session length (h).
  \textbf{G.--L. Features from Dataset 2.}  Analogous format to Panels
  A--F.}
\label{fig:supplemental_6}
\end{figure}

\bibliography{CDL-bibliography/memlab}
\bibliographystyle{CSE}
% \newpage
% \renewcommand{\refname}{Supplemental references}
% \bibliography{memlab}
